Asssesment of zonal symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2020-10-02 analysis/paper/paper.Rmd
agrega datastatement

A version-controlled repository of the code used to create this analysis can be found at https://github.com/eliocamp/asymsam.

@@

>>>>

@@

\datastatement
All data used in this paper is freely available in their respective sources. ERA5 data can be obtained via the Copernicus Climate Data Store (https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means). NOAAGlobalTemp and GPCC precipitation data can be obtained through the NOAA Physical Sicences Laboratory website (https://psl.noaa.gov/data/gridded/data.noaaglobaltemp.html and https://psl.noaa.gov/data/gridded/data.gpcc.html). The Oceanic Niño Index is avaiable via NOAA's Climate Precidction Center: https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at https://github.com/eliocamp/asymsam.

### 2020-10-02 analysis/paper/paper.tex
agrega datastatement

>>>>

\datastatement

All data used in this paper is freely available in their respective
sources. ERA5 data can be obtained via the Copernicus Climate Data Store
(https://cds.climate.copernicus.eu/cdsapp\#!/dataset/reanalysis-era5-pressure-levels-monthly-means).
NOAAGlobalTemp and GPCC precipitation data can be obtained through the
NOAA Physical Sicences Laboratory website
(https://psl.noaa.gov/data/gridded/data.noaaglobaltemp.html and
https://psl.noaa.gov/data/gridded/data.gpcc.html). The Oceanic Niño
Index is avaiable via NOAA's Climate Precidction Center:
https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/ensostuff/detrend.nino34.ascii.txt

A version-controlled repository of the code used to create this
analysis, including the code used to download the data can be found at
https://github.com/eliocamp/asymsam.
